---
title: "Data Preperation"
author: "Ioannis Ioanndis"
date: "2023-08-9"
output: pdf_document
---

# Data Preperation 

From the `Data` file, our data consist from `3` main files : 

`Sex_harrassment.csv` That contains the points of the attacks in the city

`Education.xlsx`: Contains attributes for the education level in the city 

`Athens_City` folder: geospatial folder contains all important files for the geospatial analysis :

 a.`.pbf`file: geodataframe. It contains attribute data associated with each shape in the shapefile. Each row in this table corresponds to a shape in the shapefile, and each column represents an attribute of the shape.

 b.`.prj`file: This file contains the coordinate system and projection information for the shapefile

 c.`.shp`file: This is the main file containing the geometry data of your spatial objects. It stores the actual shapes (points, lines, polygons) along with their attributes. 

 d.`.shx` file: This is the shape index file. It contains the index of the geometry records in the shapefile.

We are going to modify this data and create a new geospatial folder that would help to proceed in the analysis.


```{r}
library(geojsonio)
library(jsonlite)
library(ggplot2)
library(maps)
library(sf)
library(readxl)
library(dplyr)
library(stringr)
library(scales)
library(tidyr)
library(foreign)
library(sfheaders)
library(openxlsx)
```


```{r}
Athens_City <- read_sf("Athens_City")
Education <- read_excel("C:/Users/ioann/OneDrive/Υπολογιστής/Geospatial Project/Data/Athens Education.xlsx")
Attacks <- read.csv("C:/Users/ioann/OneDrive/Υπολογιστής/Geospatial Project/Data/SexharassmentAthens.csv")
```




We see that the English names its contained in the geodataframe `Athens_City` in the variable `display_na`.
Moreover, in the case of the `Education` the names of the regions are contained in the variable `Administrative Regions` in the Greek language. Therefore we need to construct a new column to the two dataframes called `Names_En` "Names in English" that would be the names of the region in English language. This column can be used as `Identifier` for the attributes of the dataframes. 
```{r}
Athens_City <- Athens_City %>%
  mutate(
    Names_En = str_extract(display_na, "(?<=Municipality of ).*?(?=, Regional)")
  )
```

The Column Names contains spaces between the characters ,something that makes it difficult for the edit of the dataframe.

change in a snake case

```{r}



Education <- Education %>% rename(Administrative_Regions=`Administrative regions`,
                                  Graduate_High_School=`Graduate High School`,
                                  Graduate_Middle_School=`Graduate Middle School`,
                                  Graduate_Primary_School=`Graduate Primary School`,
                                  Quit_primary_school=`Quit primary School`,
                                  Not_Ranked=`Not ranked`)
```


The data is collected by the *Hellenic Statistical Authority*, therefore it consist from variables that are writen in greek languange. We are going to create a new column `Names_En`to both `Athens_City` dataframe and `Education` dataframe that it will contain the sort name of municipalities in English and is going to be use as an Indetifier between geodata and dataframes.


- `ΔΗΜΟΣ ΑΘΗΝΑΙΩΝ`:Municipality of Athens, Regional Unit of Central Athens
- `ΔΗΜΟΣ ΒΥΡΩΝΟΣ`:Municipality of Vyronas
- `ΔΗΜΟΣ ΓΑΛΑΤΣΙΟΥ`:Municipality of Galatsi
- `ΔΗΜΟΣ ΔΑΦΝΗΣ - ΥΜΗΤΤΟΥ`:Municipality of Dafni- Ymittos
- `ΔΗΜΟΣ ΖΩΓΡΑΦΟΥ`:Municipality of Zografos
- `ΔΗΜΟΣ ΗΛΙΟΥΠΟΛΕΩΣ`:Municipality of Ilioupoli
- `ΔΗΜΟΣ ΚΑΙΣΑΡΙΑΝΗΣ`:Municipality of Kaisariani
- `ΔΗΜΟΣ ΦΙΛΑΔΕΛΦΕΙΑΣ - ΧΑΛΚΗΔΟΝΟΣ`:Municipality of Nea Philadelfia - Nea Chalkidona
- `ΔΗΜΟΣ ΑΜΑΡΟΥΣΙΟΥ`:Municipality of Marousi,
- `ΔΗΜΟΣ ΑΓΙΑΣ ΠΑΡΑΣΚΕΥΗΣ`:Municipality of Agia Paraskevi
- `ΔΗΜΟΣ ΒΡΙΛΗΣΣΙΩΝ`:Municipality of Vrilissia
- `ΔΗΜΟΣ ΗΡΑΚΛΕΙΟΥ`:Municipality of Iraklio Attikis
- `ΔΗΜΟΣ ΚΗΦΙΣΙΑΣ`:Municipality of Kifisia
- `ΔΗΜΟΣ ΛΥΚΟΒΡΥΣΗΣ - ΠΕΥΚΗΣ`:Municipality of Likovrisi - Pefki
- `ΔΗΜΟΣ ΜΕΤΑΜΟΡΦΩΣΕΩΣ`:Municipality of Metamorfosi
- `ΔΗΜΟΣ ΝΕΑΣ ΙΩΝΙΑΣ`:Municipality of Nea Ionia
- `ΔΗΜΟΣ ΠΑΠΑΓΟΥ - ΧΟΛΑΡΓΟΥ`:Municipality of Papagos - Cholargos
- `ΔΗΜΟΣ ΠΕΝΤΕΛΗΣ`:Municipality of Penteli
- `ΔΗΜΟΣ ΦΙΛΟΘΕΗΣ - ΨΥΧΙΚΟΥ`:Municipality of Filothei - Psychiko
- `ΔΗΜΟΣ ΧΑΛΑΝΔΡΙΟΥ`:Municipality of Chalandri
- `ΔΗΜΟΣ ΠΕΡΙΣΤΕΡΙΟΥ`:Municipality of Peristeri
- `ΔΗΜΟΣ ΑΓΙΑΣ ΒΑΡΒΑΡΑΣ`:Municipality of Agia Varvara
- `ΔΗΜΟΣ ΑΓΙΩΝ ΑΝΑΡΓΥΡΩΝ - ΚΑΜΑΤΕΡΟΥ`:Municipality of Agioi Anargyroi-Kamatero
- `ΔΗΜΟΣ ΑΙΓΑΛΕΩ`:Municipality of Aigaleo
- `ΔΗΜΟΣ ΙΛΙΟΥ`:Municipality of Ilion
- `ΔΗΜΟΣ ΠΕΤΡΟΥΠΟΛΕΩΣ`:Municipality of Petroupoli
- `ΔΗΜΟΣ ΧΑΪΔΑΡΙΟΥ`:Municipality of Chaidari
- `ΔΗΜΟΣ ΚΑΛΛΙΘΕΑΣ`:Municipality of Kallithea
- `ΔΗΜΟΣ ΑΓΙΟΥ ΔΗΜΗΤΡΙΟΥ`:Municipality of Agios Dimitrios
- `ΔΗΜΟΣ ΑΛΙΜΟΥ`:Municipality of Alimos
- `ΔΗΜΟΣ ΓΛΥΦΑΔΑΣ`:Municipality of Glyfada
- `ΔΗΜΟΣ ΕΛΛΗΝΙΚΟΥ - ΑΡΓΥΡΟΥΠΟΛΗΣ`:Municipality of Elliniko - Argyroupoli
- `ΔΗΜΟΣ ΜΟΣΧΑΤΟΥ - ΤΑΥΡΟΥ `:Municipality of Moschato-Tavros
- `ΔΗΜΟΣ ΝΕΑΣ ΣΜΥΡΝΗΣ`:Municipality of Nea Smyrni
- `ΔΗΜΟΣ ΠΑΛΑΙΟΥ ΦΑΛΗΡΟΥ`:Municipality of Palaio Faliro  

Create a new column that gives the English name of the municipality:
```{r}
municipality_names <- list("ΔΗΜΟΣ ΑΘΗΝΑΙΩΝ"= "Athens",
"ΔΗΜΟΣ ΒΥΡΩΝΟΣ" = "Vyronas",
"ΔΗΜΟΣ ΓΑΛΑΤΣΙΟΥ" = "Galatsi",
"ΔΗΜΟΣ ΔΑΦΝΗΣ - ΥΜΗΤΤΟΥ"= "Dafni - Ymittos",
"ΔΗΜΟΣ ΖΩΓΡΑΦΟΥ" =  "Zografos",
"ΔΗΜΟΣ ΗΛΙΟΥΠΟΛΕΩΣ" =  "Ilioupoli",
"ΔΗΜΟΣ ΚΑΙΣΑΡΙΑΝΗΣ" =  "Kaisariani",
"ΔΗΜΟΣ ΦΙΛΑΔΕΛΦΕΙΑΣ - ΧΑΛΚΗΔΟΝΟΣ"=  "Nea Philadelfia - Nea Chalkidona",
"ΔΗΜΟΣ ΑΜΑΡΟΥΣΙΟΥ"= "Marousi",
"ΔΗΜΟΣ ΑΓΙΑΣ ΠΑΡΑΣΚΕΥΗΣ"= "Agia Paraskevi",
"ΔΗΜΟΣ ΒΡΙΛΗΣΣΙΩΝ"= "Vrilissia",
"ΔΗΜΟΣ ΗΡΑΚΛΕΙΟΥ"= "Iraklio Attikis",
"ΔΗΜΟΣ ΚΗΦΙΣΙΑΣ"= "Kifisia",
"ΔΗΜΟΣ ΛΥΚΟΒΡΥΣΗΣ - ΠΕΥΚΗΣ"= "Likovrisi - Pefki",
"ΔΗΜΟΣ ΜΕΤΑΜΟΡΦΩΣΕΩΣ"= "Metamorfosi",
"ΔΗΜΟΣ ΝΕΑΣ ΙΩΝΙΑΣ"= "Nea Ionia",
"ΔΗΜΟΣ ΠΑΠΑΓΟΥ - ΧΟΛΑΡΓΟΥ"= "Papagos - Cholargos",
"ΔΗΜΟΣ ΠΕΝΤΕΛΗΣ"="Penteli",
"ΔΗΜΟΣ ΦΙΛΟΘΕΗΣ - ΨΥΧΙΚΟΥ"= "Filothei - Psychiko",
"ΔΗΜΟΣ ΧΑΛΑΝΔΡΙΟΥ"= "Chalandri",
"ΔΗΜΟΣ ΠΕΡΙΣΤΕΡΙΟΥ"= "Peristeri",
"ΔΗΜΟΣ ΑΓΙΑΣ ΒΑΡΒΑΡΑΣ"= "Agia Varvara",
"ΔΗΜΟΣ ΑΓΙΩΝ ΑΝΑΡΓΥΡΩΝ - ΚΑΜΑΤΕΡΟΥ"= "Agioi Anargyroi-Kamatero",
"ΔΗΜΟΣ ΑΙΓΑΛΕΩ"= "Aigaleo",
"ΔΗΜΟΣ ΙΛΙΟΥ"= "Ilion",
"ΔΗΜΟΣ ΠΕΤΡΟΥΠΟΛΕΩΣ"= "Petroupoli",
"ΔΗΜΟΣ ΧΑΪΔΑΡΙΟΥ"= "Chaidari",
"ΔΗΜΟΣ ΚΑΛΛΙΘΕΑΣ"= "Kallithea",
"ΔΗΜΟΣ ΑΓΙΟΥ ΔΗΜΗΤΡΙΟΥ"="Agios Dimitrios",
"ΔΗΜΟΣ ΑΛΙΜΟΥ"= "Alimos",
"ΔΗΜΟΣ ΓΛΥΦΑΔΑΣ"= "Glyfada",
"ΔΗΜΟΣ ΕΛΛΗΝΙΚΟΥ - ΑΡΓΥΡΟΥΠΟΛΗΣ"= "Elliniko - Argyroupoli",
"ΔΗΜΟΣ ΜΟΣΧΑΤΟΥ - ΤΑΥΡΟΥ" = "Moschato-Tavros",
"ΔΗΜΟΣ ΝΕΑΣ ΣΜΥΡΝΗΣ"= "Nea Smyrni",
"ΔΗΜΟΣ ΠΑΛΑΙΟΥ ΦΑΛΗΡΟΥ"= "Palaio Faliro")
```



```{r}
# corispond the English names to the dataframe
Education$Names_En <- unlist(unname(municipality_names[match(Education$Administrative_Regions, names(municipality_names))]))
```

Put the `Names_En` as first column
```{r}
Education <- Education %>% select(Names_En,everything())
```

## Missing values

At first we are going to examine the missing values of the data , meaning the individuals that their education level doesn't appear to the demographic data. In the dataframe **Education**  has the column **Not_Ranked** that indicates the population of those individuals. We are going to examine it as a percentage of the population of each region. 


The sum of the population of all the levels plus `Not Ranked`is find it in the variable *Total*

Indeed,
```{r}
education_levels <- c("PhDs_Master_Universities","Colleges",
                         "Graduate_High_School","Graduate_Middle_School",
                         "Graduate_Primary_School","Quit_primary_school","Not_Ranked")
```

```{r}
Education %>% select(education_levels) %>% all(rowSums(.)==Education$Total)
```


Calculate the percentage of the `Not_Ranked` respect to total population
```{r}
Education <- Education %>% mutate(Not_Ranked_pct=Not_Ranked/Total)
```

```{r}
summary(Education$Not_Ranked_pct)
ggplot(data=Education, aes(reorder(Names_En, Not_Ranked_pct), y=Education$Not_Ranked_pct)) +
  geom_bar(stat="identity", color="black", fill="tomato")+
  coord_flip()+
  scale_y_continuous(labels = percent_format())+
  labs(title = "Not Ranked",
       subtitle = "in % of Total Polulation",
       x= "Municipality",
       y="precent")
boxplot(Education$Not_Ranked_pct,col = "tomato")

```

We ditect that the averange of the missing population of every region is close to  6%  that it is not pass the 8%.
That means that around 6% of the population missing the data for their education level.
**Therefore we are going to exclude them from the analysis**


>We are going to create a new variable of total population that will **exclude the not ranked population**. 
From that We are going to compute the percentage of the education levels of each municipality.

```{r}
Education <- Education %>% mutate(adjust_Total=Total- Not_Ranked)

```

Finally we are going to create percentage for all the educational levels with the new adjust total

```{r}
# Adjusting  the population/ Exclude the Not Ranked 
Education <- Education %>% mutate(Uni_Degrees_pct= PhDs_Master_Universities/adjust_Total,
                                  Colleges_pct= Colleges/adjust_Total,
                                  High_School_pct= Graduate_High_School/adjust_Total,
                                  Middle_School_pct=Graduate_Middle_School/adjust_Total,
                                  Primary_School_pct=Graduate_Primary_School/adjust_Total,
                                  Quit_pct=Quit_primary_school/adjust_Total)
```
We consider also an cut-off point of the education level. That would be te *Population that has finished secondary education*. That means all people that have graduate at least from the high school. This includes people that graduates from : `High School`, `College`, `University`

```{r}
Education <-  Education %>%  mutate(Finish_Secondary_pct = 
                                      (PhDs_Master_Universities+Colleges+Graduate_High_School)/adjust_Total )
```




## Population

 whole population is 
```{r}
totalPopulation <- sum(Education$Total)
totalPopulation
```
Calculate the percent of the population of regions respect to the total population of the city.
```{r}
Education <- Education %>% mutate(Total_pct = Total/totalPopulation)
```




- Create Serial Number

Create a serial number column for every region 

```{r}
Education$SerialNumber <- seq_len(nrow(Education))
```
```{r}
serial <- Education %>% select(SerialNumber,Names_En)
```

```{r}
Athens_City <- left_join(Athens_City,serial, by = "Names_En")
```

Trasport the `Finish_Secondary_pct` column also to the geodataframe `Athens_City`

```{r}
df <-  Education %>% select(Names_En,Finish_Secondary_pct)
Athens_City <- left_join(Athens_City,df, by = "Names_En")
```



See if the column `Names_En` and `SerialNumber`of both dataframes `Athens_City` and `Education` are indentical
```{r}
print(identical(sort(Athens_City$Names_En), sort(Education$Names_En)))
print(identical(sort(Athens_City$SerialNumber), sort(Education$SerialNumber)))
```

## Attack Points

We modify the `Attack_Points` with the correct coordinates system
```{r}

Attack_Points <- st_as_sf(Attacks, coords = c("X", "Y"), crs = 4326)
```

Those are points from all over the country. We need only the points that are in the city of Athens. We are going to find them with intersection.

 Find points that intersect with the geospatial multipolygon
```{r}

Attack_Points <- st_intersection(Attack_Points, Athens_City)
```

```{r}
df <- Athens_City %>% select(SerialNumber,Names_En,display_na,geometry)
```

```{r}
Attack_Points1 <- st_join(Attack_Points, df, join = st_within)
```

Now , the dataframe`Attack_Points1` contains all the points of that an attack was occured. What we interest is the amount of the attacks on each region. Therefore, we are going to extract the names , and create a column in `Education` that contains the number of attacks to each region.
```{r}
vector_incident <- Attack_Points1$Names_En.x
```



```{r}
count <- table(vector_incident)
Count_Points <- data.frame(Names_En = names(count),count_points = as.numeric(count))
```

```{r}
dim(Count_Points)
```
We see that one region missing (no attacks in that region). We are going to insert to this region the number 0 (zero attacks)
```{r}
Education <- left_join(Education,Count_Points,by = "Names_En")

```

Put in the front the columns 
```{r}
Education <- Education %>% select(SerialNumber,Names_En,count_points,everything())
```

```{r}
Education <- Education %>%   mutate(count_points = ifelse(is.na(count_points), 0, count_points))
```
Pass the `count_points` also to the geodataframe `Athens_City`

```{r}
pointsc <-  Education %>% select(Names_En,count_points)

Athens_City <- left_join(Athens_City,pointsc,by = "Names_En")
```


Reorder the dataframes
```{r}


# Reorder columns so SerialNumber comes first
Education <- Education %>%select(SerialNumber,Names_En,count_points,Finish_Secondary_pct,everything())
Athens_City <- Athens_City %>%select(SerialNumber,Names_En,count_points,Finish_Secondary_pct,everything())


```
## Save the new files 

```{r }
path <- "C:/Users/ioann/OneDrive/Υπολογιστής/Geospatial Project/"
write.xlsx(Education, file = paste0(path,"Education_Prepared.xlsx"))


```

```{r}
write_sf(Attack_Points1,paste0(path,"Attack_Points.geojson"))
```

```{r}
write_sf(Athens_City,paste0(path,"Athens_City_Prepared.geojson"))
```

