---
title: "Moran Index Analysis"
author: "Ioannis Ioanndis"
date: "2023-05-04"
output: html_document
---

# Moran Index Analysis

## Moran's Index Definition
 
The Moran's I Index is a statistical measure used in geographical analysis and statistics to evaluate spatial autocorrelation, which is the degree to which the values of a variable are associated with the values of the same variable in nearby geographic regions or spatial units. It assists researchers and analysts in determining if a pattern of similarity or dissimilarity exists in the distribution of a specific property across a geographic area.
It is employed to:
Identifies geographical patterns in data to determine if clustering or dispersion is required.
Specify whether comparable values are grouped together or spread randomly.
If there is evidence of spatial dependency, which means that local places are more likely to be similar than distant locations.

```{r}
library(spdep) 
library(sf)
library(tmap) 
library(leaflet)
library(readxl)
library(ggplot2)
library(dplyr)
library(spatialreg)
```
## Load the data 
```{r }
Athens_City <- st_read("Geodata")
```
```{r}
Attack <- st_read("Attack_Points.geojson")
```

```{r}
Education <- read_excel("Education_Prepared.xlsx")
```


```{r}
names(Athens_City)
```

We are going to rename the `Finish_Secondary_pct` to shorter `edu`
```{r}
Athens_City <- Athens_City %>% rename(SerialNumber = SerialNumb,count_points =count_poin,edu =Finish_Sec)
```


## Define spatial Neighbours 

First we must clarify which spatial units can be consider as neighbours. Most common approach, is to difine by distance of two spatia-units or from a common boundary. There are multiple ways for that definition,such as k-nearest neighbours , critical cut-off distance , contiguity -based. It also be needed to be defined a representative point for each spatial - unit. A main choise is the centroid of the region.

```{r}
coords <- st_centroid(st_geometry(Athens_City))
```

# Global Moran Index Analysis 

In global autocorrelation analysis we examine autocorrelation in the entire dataset (all regions). Therefore we choose to pick neighbours with *critical cut-off distance* method.

First we must find the the minimum threshold distance which allows all regions to have at least one neighbour.

We are going to calculate the k-NN with k= 1 (giving one neighbour to each region) and using as threshold the maximum of it. (Therefore everyone will have at least on neighbour).
```{r}
knn1ATH <- knn2nb(knearneigh(coords,k=1))
all.linkedT <- max(unlist(nbdists(knn1ATH, coords))) 
all.linkedT
```

We found that the maximum k-NN is `5.152077`. We are going to use `5.16`



## Define spatial weights

```{r}
dnb516 <- dnearneigh(coords, 0, 5.16)

dnb516.listw <- nb2listw(dnb516,style="W")
```

##Plotting

```{r}
plot(st_geometry(Athens_City), border="grey") 
title(main="d nearest neighbours, d = 5.16 km") 
plot(dnb516, coords, add=TRUE, col="blue")
```
## Moran Index test of spatial autocorrelation (global)

We perfom Moran Index I for spatial autocorrelation for the two variables `count_points` that are the amount of sexual harrassment attacks in each region and for `Finish_Secondary_pct` that counts the percentage of the people of the region finished at least secondary education.

Under the normality assumption 
```{r}
moran.test(Athens_City$count_poin, dnb516.listw, randomisation=FALSE)
```
```{r}
moran.test(Athens_City$edu, dnb516.listw, randomisation=FALSE)
```

The results gives for :

sexual harassment attacks: p-value = 40.02%  We cannot declare any correlation between the regions regarding the attacks
education level (graduate secodary education) : p-value << 5% that the education level is indeed related by the region.

- with randomisation

```{r}
moran.test(Athens_City$count_points, dnb516.listw, randomisation=TRUE)
```
```{r}
moran.test(Athens_City$edu, dnb516.listw, randomisation=TRUE)
```
In randomisation we see that we come in the same conclusion.


# Descriptive spatial statistics for areal data (local analysis)

Moran Index I test can global can captures a global pattern of the autocorrelation , in the whole dataset but we may interest to find clusters of regions inside the dataset. 




## Moran scatterplot

We are going to use moran scatterplot in order to indentify the regions that influence the most the local area. In Moran scatterplot the areas with the most influence are marked 
```{r}
mplot_edu <- moran.plot(Athens_City$edu, listw=dnb516.listw,
                        main="Moran scatterplot",
                        xlab = "Finish Secondary Education",
                        ylab = "Lagged")
grid()
```
We can see 3 areas in the education level that influence the most.

```{r}
mplot_att <- moran.plot(Athens_City$count_points, listw=dnb516.listw, 
                        main="Moran scatterplot",
                        xlab = "Attacks",
                        ylab = "Lagged")
grid()
```
2 areas to the attack points. Let plot on map to visualise the areas 
```{r}
Athens_City$hat_value_edu <- mplot_edu$hat
tm_shape(Athens_City) + tm_polygons("hat_value_edu") +tm_layout(title = "Education")
 
```

```{r}
Athens_City$hat_value_att <- mplot_att$hat
tm_shape(Athens_City) + tm_polygons("hat_value_att")+tm_layout(title = "Attacks")

```


```{r}
mplot_edu <- moran.plot(Athens_City$edu, listw=dnb516.listw, main="Moran scatterplot", 
         return_df=F)
mplot_att <- moran.plot(Athens_City$count_points, listw=dnb516.listw, main="Moran scatterplot", 
         return_df=F)
hotspot_edu <- as.numeric(row.names(as.data.frame(summary(mplot_edu))))

hotspot_att <- as.numeric(row.names(as.data.frame(summary(mplot_att))))

```

```{r}
Athens_City$wx_edu <- lag.listw(dnb516.listw, Athens_City$edu)
Athens_City$wx_att <- lag.listw(dnb516.listw, Athens_City$count_points)
```




```{r}
Athens_City$quadrant_edu <- rep("None", length(Athens_City$edu))
for(i in 1:length(hotspot_edu))  {
  if (Athens_City$edu[hotspot_edu[i]]>mean(Athens_City$edu) & Athens_City$wx_edu[hotspot_edu[i]]> mean(Athens_City$wx_edu)) 
        Athens_City$quadrant_edu[hotspot_edu[i]] <- "HH" 
  if (Athens_City$edu[hotspot_edu[i]]>mean(Athens_City$edu) & Athens_City$wx_edu[hotspot_edu[i]]< mean(Athens_City$wx_edu)) 
        Athens_City$quadrant_edu[hotspot_edu[i]] <- "HL" 
  if (Athens_City$edu[hotspot_edu[i]]<mean(Athens_City$edu) & Athens_City$wx_edu[hotspot_edu[i]]<mean(Athens_City$wx_edu)) 
        Athens_City$quadrant_edu[hotspot_edu[i]] <- "LL" 
  if (Athens_City$edu[hotspot_edu[i]]<mean(Athens_City$edu) & Athens_City$wx_edu[hotspot_edu[i]]>mean(Athens_City$wx_edu)) 
        Athens_City$quadrant_edu[hotspot_edu[i]] <- "LH" 
  }
table(Athens_City$quadrant_edu)

```


```{r}
Athens_City$quadrant_att <- rep("None", length(Athens_City$count_points))
for(i in 1:length(hotspot_att))  {
  if (Athens_City$count_points[hotspot_att[i]]>mean(Athens_City$count_points) & Athens_City$wx_att[hotspot_att[i]]> mean(Athens_City$wx_att)) 
        Athens_City$quadrant_att[hotspot_att[i]] <- "HH" 
  if (Athens_City$count_points[hotspot_att[i]]>mean(Athens_City$count_points) & Athens_City$wx_att[hotspot_att[i]]< mean(Athens_City$wx_att)) 
        Athens_City$quadrant_att[hotspot_att[i]] <- "HL" 
  if (Athens_City$count_points[hotspot_att[i]]<mean(Athens_City$count_points) & Athens_City$wx_att[hotspot_att[i]]<mean(Athens_City$wx_att)) 
        Athens_City$quadrant_att[hotspot_att[i]] <- "LL" 
  if (Athens_City$count_points[hotspot_att[i]]<mean(Athens_City$count_points) & Athens_City$wx_att[hotspot_att[i]]>mean(Athens_City$wx_att)) 
        Athens_City$quadrant_att[hotspot_att[i]] <- "LH" 
  }
table(Athens_City$quadrant_att)

```
```{r}
tm_shape(Athens_City) + tm_polygons("quadrant_edu") + tm_layout(title = "Education")
```
```{r}
tm_shape(Athens_City) + tm_polygons("quadrant_att") + tm_layout(title = "Attacks")
```
The results give :
For the Education Level:
 That have "High-High" and "Low -Low"   in moran scatterplot meaning that we have positive autocorrelation
 On the other hand  in Attacks we have two regions, one "High-Low" and one "Low - High" considering as negative autocorrelation.
 
# Local Moran Index Analysis

We are going to see the significance of the visual results 

```{r}
lmI_edu <- localmoran(Athens_City$edu, dnb516.listw)
head(lmI_edu)
```


```{r}
lmI_att <- localmoran(Athens_City$count_points, dnb516.listw)
head(lmI_att)
```


```{r}
Athens_City$lmI_edu <- lmI_edu[,1]

tm_shape(Athens_City) + 
  tm_polygons("lmI_edu") +
  tm_layout(title = "Local Moran's I values (Education)",title.size = 1.1)


```
It can be noticed, that regions in the far West part and Far East part of the city have high Moran 's I values for the variable of the education. That can be noticed also from the global analysis and the plotting in `Data Exploration` that the region in the west have low values in the education compare to the averange , where in the east higher than the averange.

```{r}
Athens_City$lmI_att <- lmI_att[,1]

tm_shape(Athens_City) + 
  tm_polygons("lmI_att") +
  tm_layout(title = "Local Moran's I values (Attacks)",title.size = 1.1)


```
In the terms of the Local Moran Index value in the variable of the attacks, Athens City center monopolize the the values , an expected results since most of the attacks occured there. 

Its important to see how much significant are those results 


```{r}
Athens_City$locmpv_edu <- p.adjust(lmI_edu[, "Pr(z != E(Ii))"], "bonferroni")
tm_shape(Athens_City) + 
    tm_polygons("locmpv_edu", title = "Local Moran's I significance map",
                breaks=c(0, 0.0005, 0.001, 0.005, 0.01, 0.05, 0.1, 0.2, 0.5, 0.75, 1)) + tm_layout(title = "Education")
```
From the results in the variable of the Education, it can be noticed , that only two regions `Peristeri` in the West and `Agia Paraskevi` in the East can be consider significant to influence:
```{r}
a <- Athens_City$locmpv_edu[which(Athens_City$Names_En =="Peristeri")]
b <- Athens_City$locmpv_edu[which(Athens_City$Names_En =="Agia Paraskevi")]

print(paste("Agia Paraskevi",a))
print(paste("Peristeri",b))
```
As a coclusion, even from the global analysis that was already shown  signinifant difference in the matter of  education between west and east .
```{r}
result_df <- tibble(Result = sig)
print(result_df)
```



```{r}
Athens_City$locmpv_att <- p.adjust(lmI_att[, "Pr(z != E(Ii))"], "bonferroni")
tm_shape(Athens_City) + 
    tm_polygons("locmpv_att", title = "Local Moran's I significance map",
                breaks=c(0, 0.0005, 0.001, 0.005, 0.01, 0.05, 0.1, 0.2, 0.5, 0.75, 1)) +tm_layout(title = "Attacks")
```

For the variable of the attacks we see that the Moran Index is not significant. Therefore we cannot assume any local influence of regions in the matter of the attacks.


# Spatial Regression

The purpose of conduct this analysis was also to estimate any influence of the education that can be occured to the number of the attacks on a region. Therefore we are going to conduct a spatial regression model.


```{r}
SDM <- lagsarlm(Athens_City$count_points~ edu, data = Athens_City, listw=dnb516.listw,
                type="mixed")
summary(SDM)
```

As been expected it cannot be proved any spatial autocorrelation of the Education and Attacks.

More precisely, 
The p-value for the spatial autoregressive parameter Rho is not significant p-value = 0.948

where also the Lagrange Multiplier test for the  spatial autocorrelation in the lag model resduals gives p-value = 0.122 not significant.
Therefore we have no evidence to prove spatial autocorrelation for the two variables *Education* and *Attacks*.


We are going to see the robustness of the model performing analysis of the impact of the variable education , conducting 100 simulation of Monte Carlo.
```{r}
impSDM <- impacts(SDM, listw=dnb516.listw, R=100)
summary(impSDM, zstats=TRUE, short=TRUE)
```

By the results we see that the impact of Education is not significant. The p-values are large to reject the null hypothesis.

To conclude, there is not any evidence of any significant impact of the Education to the attacks.

